Proposed Solution

### 2016-11-14 Ennan-Proposal/intro.tex
stuff

Configuration errors (i.e., misconfigurations) have become one of the major causes of software failures, resulting in security vulnerabilities, application outages, and incorrect program executions. 
Configuration errors accounted for the largest portion of failures in storage systems in a 2014 industry survey, and misconfigurations were also independently reported as the main cause of Hadoop cluster failures. 
Although many techniques have been proposed to automate configuration error detection, these approaches rely heavily on manual efforts. 
Since the dependencies and constraints in configuration files are often subtle and implicit, this is a time consuming and error prone task to do by hand.
Current configuration verification tools require the users to explicitly define constraints, and equally onerous task.

>>>>

Configuration errors (also known as misconfigurations) have become one of the major causes of system failures, resulting in security vulnerabilities, application outages, and incorrect program executions. 
Configuration errors were reported to be the largest fraction of failures in storage systems in a 2014 industry survey. Although many techniques have been proposed to automate configuration error detection, these approaches mainly /aaosksadjklsal

rely heavily on manual efforts. 
Since the dependencies and constraints in configuration files are often subtle and implicit, this is a time consuming and error prone task to do by hand.
Current configuration verification tools require the users to explicitly define constraints, and equally onerous task.

### 2016-11-14 Ennan-Proposal/travis.tex
stuff

From this summary we can then build a model $M(P_t)$, as in \app,
which is the full set of possible relations derivable 
from the program summary.
Again, the user must provide templates for the learning process.

We will denote the build status returned from TravisCI when run on $P_t$ with $S(P_t)$.
Any files with a $Pass$ build status are correct, and any files with an $Err$ build status are incorrect.
%In this application, we consider all non-erroring build status to be passing, denoted $Pass$ and otherwise $Err$.
For brevity, we denote sequences of build statuses with the following notation:
\begin{align*}
  S(P_t)=Pass \land S(P_{t+1})=Err \implies S(P_{t,t+1}) = PE
\end{align*}

@@

We then can combine Eq \ref{eq:E}, \ref{eq:P}, and \ref{eq:PE} with
conjunctions and ask a SMT solver for a model satisfying the formula.
The resulting model will be the sets of necessary rules ($Nec$), and the set of breaking rules ($Br$), which can be used to check new configuration files.
Since we used a similar model to \app, we will still be able to provide justifications for the classification results.

>>>>

From these summaries we will build a model $M(P_t)$, using the same techniques as in 
\app. $M(P_t)$ actually is a set of all possible relations derivable 
from the program summary. As previously, we need to construct templates for the 
learning process, since the level of specification details depends on them.

We now outline how we plan to use SMT solvers to find the sets of necessary rules ($Nec$), and the set of breaking rules ($Br$).

Let $S(P_t)$ be the build status returned from TravisCI when run on $P_t$.
It can be either $Pass$ or $Err$. We define shorthand $S(P_{t,t+1}) = PE$ to 
state that the program was compiling before and now it does not:
\begin{align*}
  S(P_{t,t+1}) = PE :\Leftrightarrow S(P_t)=Pass \land S(P_{t+1})=Err 
\end{align*}

@@

We then can combine \eqref{eq:E}, \eqref{eq:P}, and  \eqref{eq:PE} with
conjunctions and ask a SMT solver for a model satisfying the formula.
The resulting model will be the sets of necessary rules ($Nec$), and the set of breaking rules ($Br$), which can be used to check new configuration files.
Since we used a similar model to \app, we will still be able to provide justifications for the classification results.
